\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Renamed FPs as impostors, to avoid confusion with false positives arising from the search. We should have been calling the Stage 2 duds impostors from the start! The term false positive should be reserved for one of the *outputs* of a search. #203

This paper is organised as follows. In
\Sref{sec:data}, we introduce the \cfhtls imaging data and the
previously published lens samples from the \cfhtls. We generated a training sample,
consisting of simulated lenses, duds and false positives, in order to
aid the \sw volunteers in the process of finding lenses. We give details of this
training sample in \Sref{sec:ts} and \Sref{sec:dfp}. In \Sref{sec:swap},
we briefly describe how the classifications of images from the volunteers are
turned into a catalog of plausible candidates (for further details, see
\PaperOne). In \Sref{sec:results}, we present the new lens candidates from \sw and
compare it to the lens samples produced by past robotic searches of
the \cfhtls. Next, we discuss what kind of lenses are detected
or missed by the algorithms and \sw in \Sref{sec:discuss}.
Our conclusions are given in \Sref{sec:conclude}.

@@

\section{Training sample: Duds and False positives}
\label{sec:dfp}

Citizen scientists need training not only to identify gravitational
lenses, but also to reject images which either have no lenses or have
objects which are lens impostors. Hence, in addition to the simulated
lenses, we added a sample of duds and false positives to the training
sample. Duds are images which have been visually inspected by experts
and confirmed to contain no lenses. False positives (FPs) are systems
which look like lenses but are not, for example, spiral galaxies,
starforming galaxies, chance alignments of features arranged in a
lensing configuration and stars.

We selected a sample of 450 duds for the \StageOne classification in \sw
and a sample of 500 false positives for the \StageTwo inspection. The
sample of false positives was selected from the candidates which passed
the \StageOne of \sw. We note that this is the first time, we have a
systematically compiled sample of visually inspected false positives by
the \sw volunteers and categorized by the science team. We produce
additional larger sample of a few thousand FPs by scanning through the
low probability images after the completion of \StageTwo. All of these
data products will be made available at
\texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Such a sample has tremendous
utility for training and testing of various lens finding algorithms
\citep[e.g.,][]{Chan2014}.

>>>>

This paper is organised as follows. In
\Sref{sec:data}, we introduce the \cfhtls imaging data and the
previously published lens samples from the \cfhtls. We generated a training sample,
consisting of simulated lenses, duds and impostors, in order to
aid the \sw volunteers in the process of finding lenses. We give details of this
training sample in \Sref{sec:ts} and \Sref{sec:dfp}. In \Sref{sec:swap},
we briefly describe how the classifications of images from the volunteers are
turned into a catalog of plausible candidates (for further details, see
\PaperOne). In \Sref{sec:results}, we present the new lens candidates from \sw and
compare it to the lens samples produced by past robotic searches of
the \cfhtls. Next, we discuss what kind of lenses are detected
or missed by the algorithms and \sw in \Sref{sec:discuss}.
Our conclusions are given in \Sref{sec:conclude}.

@@

\section{Training sample: Duds and Impostors}
\label{sec:dfp}

Citizen scientists need training not only to identify gravitational
lenses, but also to reject images which either contain no lenses, or contain
objects which could be mistaken for lenses. Hence, in addition to the simulated
lenses, we added a sample of ``duds'' and ``impostors'' to the training
sample. Duds are images which have been visually inspected by experts
and confirmed to contain no lenses. Impostors are systems
which look like lenses but are not, for example, spiral galaxies,
starforming galaxies, chance alignments of features arranged in a
lensing configuration and stars.

We selected a sample of 450 duds for the \StageOne classification in \sw
and a sample of 500 impostors for the \StageTwo inspection. The
sample of impostors was selected from the candidates which passed
the \StageOne of \sw. We note that this is the first time we have a
systematically compiled sample of visually inspected impostors by
the \sw volunteers and categorized by the science team. We produce
additional larger sample of a few thousand FPs by scanning through the
low probability images after the completion of \StageTwo. All of these
data products will be made available at
\texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Such a sample has tremendous
utility for training and testing of various lens finding algorithms
\citep[e.g.,][]{Chan2014}.
